---
title: Financial Risk Management
subtitle: Derivatives
author: "Jiahua (Java) Xu, Ph.D."
date: "`r format(Sys.time(), '%Y')`"
classoption: aspectratio=169    
output:
  beamer_presentation:
    slide_level: 2
    theme: Dresden
    keep_tex: no
    toc: false
    incremental: false
    colortheme: beaver
    fonttheme: structurebold
    highlight: haddock
    includes:
      in_header: diss-beamer.sty
  ioslides_presentation:
    logo: figure/ucllogo.svg
  slidy_presentation:
    footer: "Derivatives"
knit: (
  function(inputFile, encoding) { 
  
    pSubTitle <- 'derivatives'
  
    rmarkdown::render( 
      input       = inputFile, 
      encoding    = encoding, 
      params      = list(sub_title = pSubTitle),      
      output_file = pSubTitle) })
link-citations: yes
# bibliography: Blockchain.bib
# suppress-bibliography: no
...

```{r echo=FALSE, warning=FALSE}
library(magrittr)
library(knitr)
library(tikzDevice)

opts_chunk$set(
  dev = 'tikz',
  fig.path = 'figure/',
  echo = FALSE,
  error = FALSE,
  cache = TRUE,
  message = FALSE,
  results = 'hide',
  warning = FALSE,
  autodep = TRUE
)
```


```{r child = 'sessions/intro.Rmd', eval=TRUE}
```

```{r child = 'sessions/forward.Rmd', eval=TRUE}
```

```{r child = 'sessions/swap.Rmd', eval=TRUE}
```


## Thank you!

**Contact**

\vspace{0.6cm}

Jiahua (Java) Xu

\vspace{0.4cm}

UCL Centre for Blockchain Technologies


66-72 Gower Street



\vspace{0.4cm}

jiahua.xu@ucl.ac.uk

<!-- ## References {.allowframebreaks} -->
<!-- \small -->

\widowpenalties 1 0